---
title: "Lab 3"
output: pdf_document
---

## Problem 1: Stepwise Regression

Load in the data:

```{r}
beer = read.csv("beer.csv")
```

Using the dataset `beer.csv`, build a model to predict beer consumption. (Hint: don't use Date as a predictor)

a. Build the model using backward elimination and produce a summary. 

```{r results = "hide"}
full = lm(Consumption ~ . -Date, data = beer)
BE = step(full)
```

```{r}
summary(BE)
```

b. Build the model using forward selection and produce a summary. 

```{r results="hide"}
null = lm(Consumption ~ 1, data = beer)
FS = step(null, scope = list(upper=full), direction = "forward")
```

```{r}
summary(FS)
```

c. Build the model using stepwise and produce a summary. 

```{r results="hide"}
SW = step(null, scope = list(upper = full), direction = "both")
```

```{r}
summary(SW)
```

d. Are the models the same?  If not, which one is different? 

*Yes, all of the models are the same. TempMax, Weekend, and Precip are used in the models.*

e. How well does the backward elimination model fit the data? 

*72.26% of the variation in Consumption is explained.*


f. Construct a residual plot and a histogram of the residuals of the backward elimination model and discuss if the linear regression model assumptions are met.

```{r}
par(mfrow=c(1, 2))
plot(BE, which = 1)
hist(BE$residuals, main = "", xlab = "Residuals")
```

*Linearity - Linearity assumption is mostly satisfied as the trend in the scatterplot is a line centered around 0.*
*Independence -  No clear violation of independence.*
*Normality - The residuals show a distribution that is approximately bell-shaped in the histogram.*
*Error variance - There appears to be constant variance centered around 0 in the residual plot, so the constant variance assumption is met.*

## Problem 2: Best Subsets

Using the dataset `beer.csv`, build a model to predict beer consumption. (Hint: don't use Date as a predictor)

a. Fit a best subsets model to predict consumption from all  predictors.

```{r}
library(leaps)
BSR = regsubsets(Consumption ~ . -Date, data=beer)
```

b. Use the plot function on the best subsets object from part a.

```{r}
plot(BSR)
```

c. Which variables are in the best subset?

*TempMax, Weekend, and Precip.*

d. Plot the best subsets object again, but include the option: scale='adjr2'.

```{r}
plot(BSR, scale = "adjr2")
```

e. Which variables are in the best subset using adjusted R squared?

*TempMax, Weekend, and Precip.*

## Problem 3: Markdown

Now you will modify your document so that it is in pristine format. Knit the document as a pdf and inspect it for neatness.